---
title: "Wikipedia 2"
output: html_document
---

#Table of Contents:

- [Introduction](#Introduction.)
- [Loading packages](#Loading Packages.)
- [Reading the data](#Reading wikipedia.)
- [Transforming the data](#Transforming Data.)
- [Further Transformations.](#Further transformations.)
- [Visualizing the data](#Visualizing variables.)

<div id='Introduction.'/>
#Introduction.

The purpose of this project is to mine data from the [Wikipedia](http://en.wikipedia.org/wiki/) website and perform classification.
This project was performed with the guidance of the following websites:
[Manipulate clusters of texts with R](https://dzone.com/articles/manipulate-clusters-of-texts)
[R : Categorization / Clustering Of Wikipedia Articles Using R](http://brazenly.blogspot.gr/2015/02/r-categorization-clustering-of.html)
[Text mining in R - Automatic categorization of Wikipedia articles](https://www.r-bloggers.com/text-mining-in-r-automatic-categorization-of-wikipedia-articles/)

<div id='Loading Packages.'/>
#Loading Packages.

The first step towards analyzing the data is Loading the packages:

```{r message=FALSE}
library(tm)
library(stringi)
library(proxy)
library(wordcloud)
```

<div id='Reading wikipedia.'/>
#Reading wikipedia.

The next step is reading wikipedia.
To perform this analysis I chose 9 articles of 3 different topics. The articles are:
- From Geography: Alaska, California, Florida
- From Mathematics: Square, Rectangular, Rhombus
- From NBA: Bulls, Bucks, Spurs
And then set up the connection with wikipedia and pulled all information:

```{r}
wiki <- "http://en.wikipedia.org/wiki/"
titles <- c("Florida",
           "California",
           "Alaska",
           "Rectangular", "Square", "Rhombus",
           "Bulls", "Bucks", "Spurs")
articles <- character(length(titles))
for (i in 1:length(titles)) {
  articles[i] = stri_flatten(readLines(stri_paste(wiki, titles[i])), col = " ")
}
```

<div id='Transforming Data.'/>
#Transforming Data.

Then we transform the "articles" into a Corpus.

```{r}
docs <- Corpus(VectorSource(articles))
```

Following the conversion to Corpus we have to clean out all unnecessary terms. These include:<br>
- Replace characters like + , . , ? etc with Space  " "<br>
- Replace tab characters (\t) with Space<br>
- Remove extra whitespaces from the documents.<br>
- Remove from the documents words which we find redundant for text.<br>
- Remove English "stopwords".<br> 
- Remove punctuation marks.<br>
- Transform characters to lower case.<br>
- Convert previous result to "PlainTextDocument".<br>

```{r}
docs <- tm_map(docs, function(x) stri_replace_all_regex(x, "<.+?>", " ")) 
docs <- tm_map(docs, function(x) stri_replace_all_fixed(x, "\t", " ")) 
docs <- tm_map(docs, stripWhitespace) 
docs <- tm_map(docs, removeWords, stopwords("english")) 
docs <- tm_map(docs, removePunctuation) 
docs <- tm_map(docs, tolower) 
docs <- tm_map(docs, PlainTextDocument) 
```

<div id='Further transformations.'/>
#Further transformations.
After Removing all unnecessary terms we can transform the Corpus above into a Document Term Matrix.

```{r}
docsTDM <- DocumentTermMatrix(docs)
```

In order to proceed with our analysis we have to convert the Document Term Matrix into a matrix.

```{r}
docsTDM2 <- as.matrix(docsTDM)
```

Then we check the dimensions of the matrix

```{r}
dim(docsTDM2) 
frequency <- colSums(docsTDM2)
frequency <- sort(frequency, decreasing=TRUE)
mots=frequency[frequency>20]
s=docsTDM2[1,which(colnames(docsTDM2) %in% names(mots))]
for(i in 2:nrow(docsTDM2)) s=cbind(s,docsTDM2[i,which(colnames(docsTDM2) %in% names(mots))])
colnames(s) <- titles
```

<div id='Visualizing variables.'/>
#Visualizing variables.

Then we can use a PCA to visualise the 'variables':

```{r include= FALSE}
library(FactoMineR)
```
```{r}
PCA(s)
```

Finally, we perform text classification with hclust() function and plot them with plot() function.

```{r}
s0=s/apply(s,1,sd)
h <- hclust(dist(t(s0)), method = "ward.D")
plot(h, labels = titles, sub = "")
```
